Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-22 Documents/supplementary_text.tex
A few tweaks to supplement.

We developed a country-level continuous-time, compartmental model that
divides people aged $15$\;y and older into non-overlapping HIV states.
We chose to consider only these ages because they are the vast
majority of PLHIV---93\% in 2014 \cite{UNICEF}---and because HIV and
demographic data are often stratified into these ages, although some
data used to parametrize the model was only available for ages
$15$--$49$ rather than for ages $15$ and older.  The background
mortality rate ($\mu$) in each of the 127 countries was collected from
published estimates \cite{World_Development_Indicators2013-ee}.  The
recruitment rate ($\kappa$) into the age $15\;\text{y}$ and older
group was set by the difference between the country's population
growth rate \cite{WorldBankpg} and its background mortality rate
\cite{World_Development_Indicators2013-ee}, as would be true if the
population was at its stable age structure.

@@

For 127 countries, we found sufficient data to parametrize our model.
Demographic data, including population growth rate \cite{WorldBankpg},
death rate \cite{World_Development_Indicators2013-ee}, and number of
people aged 15--49 years \cite{The_World_Bank2016-fd} were obtained
from the World Bank (Table S2). Longitudinal HIV prevalence (Table S3)
and incidence (Table S4) estimates for ages 15--49, spanning from as
early as 1990 to 2015, were primarily derived from the AIDSinfo
database produced by UNAIDS \cite{Unaids2016-an}. Other sources
included UNAIDS Country Progress Reports \cite{Unaids2016-am}
published from 2012 to 2016 and AIDS Data Hub \cite{AIDSdatahub-fg},
which compiles data from UNAIDS, UNICEF, WHO, and the Asian
Development Bank. These sources were also used to inform the initial
conditions for the model: the number of people diagnosed with HIV, the
number on ART, and the number who have viral suppression or have been
retained on treatment for at least 12 months (Table S5). Where data
were not available from these sources, alternative resources such as
peer-reviewed journal articles and country health ministry reports
were consulted.  See Tables S2--S6 for full information on data
sources for each country.  The data tables are also available in the
public source-code repository \cite{medlock2016-git}.

>>>>

We developed a country-level continuous-time, compartmental model that
divides people aged $15$\;y and older into non-overlapping HIV states.
We chose to consider only these ages because they are the vast
majority of global PLHIV---93\% in 2014 \cite{UNICEF}, because HIV and
demographic data are often stratified into ages $15$--$49$, and to
capture the continuing burden of infections in people ages $50$ and
older.

The background mortality rate ($\mu$) in each of the
127 countries was collected from published estimates
\cite{World_Development_Indicators2013-ee}.  The recruitment rate
($\kappa$) into the age $15\;\text{y}$ and older group was set by the
difference between the country's population growth rate
\cite{WorldBankpg} and its background mortality rate
\cite{World_Development_Indicators2013-ee}, as would be true if the
population was at its stable age structure.

@@

For 127 countries, we found sufficient data to parametrize our model.
Demographic data, including population growth rate \cite{WorldBankpg},
death rate \cite{World_Development_Indicators2013-ee}, and number of
people aged 15--49 years \cite{The_World_Bank2016-fd} were obtained
from the World Bank (Table S2). Longitudinal HIV prevalence (Table S3)
and incidence (Table S4) estimates for ages 15--49, spanning from as
early as 1990 to 2015, were primarily derived from the AIDSinfo
database produced by UNAIDS \cite{Unaids2016-an}. Other sources
included UNAIDS Country Progress Reports \cite{Unaids2016-am}
published from 2012 to 2016 and AIDS Data Hub \cite{AIDSdatahub-fg},
which compiles data from UNAIDS, UNICEF, WHO, and the Asian
Development Bank. These sources were also used to inform the initial
conditions for the model: the number of people diagnosed with HIV, the
number on ART, and the number who have viral suppression or have been
retained on treatment for at least 12 months (Table S5). Where data
were not available from these sources, alternative resources such as
peer-reviewed journal articles and country health ministry reports
were consulted.  See Tables S2--S5 for full information on data
sources for each country.  The data tables are also available in the
public source-code repository \cite{medlock2016-git}.
